Quantifying the home ground advantage with `hyper2` and `hyper3` objects

### 2025-02-11 inst/home_advantage.Rmd
slight rewording

Showing convincingly that we may reject the null that $p_1=p_2$ and
assert that the players do in fact differ in strength, at least with
this value of $\lambda$.  Observe that a naive analysis would have
$p_1$ winning $w=A+C=`r A+C`$ games and losing $l=B+D=`r B+D`$ games,
from which we would obtain $\hat{p_1}=`r A+C`/`r A+B+C+D`$; a
likelihood ratio for $H_0\colon p_1=0.5$ would be

@@

Agresti considers a dataset of seven baseball teams who play one
another repeatedly.  Each game is played at the home ground of one
team, the other playing away.  The dataset is as follows:

```{r,label=makeAgrestimatrix}
baseball_table <- matrix(c(
NA,   4+3i, 4+2i, 4+3i, 6+1i, 4+2i, 6+0i,
3+3i, NA  , 4+2i, 4+3i, 6+0i, 6+1i, 4+3i,
2+5i, 4+3i, NA  , 2+4i, 4+3i, 4+2i, 6+0i,
3+3i, 5+1i, 2+5i, NA  , 4+3i, 4+2i, 6+1i,
5+1i, 2+5i, 3+3i, 4+2i, NA  , 5+2i, 6+0i,
2+5i, 3+3i, 3+4i, 4+3i, 4+2i, NA  , 2+4i,
2+5i, 1+5i, 1+6i, 2+4i, 1+6i, 3+4i, NA),7,7)
teams <- c("Milwaukee", "Detroit", "Toronto", "New York", "Boston","Cleveland","Baltimore")
rownames(baseball_table) <- teams
colnames(baseball_table) <- teams
M <- baseball_table # saves typing
```

>>>>

Showing that we fail to reject the null that $p_1=p_2$, at least with
this value of $\lambda$.  Observe that a naive analysis would have
$p_1$ winning $w=A+C=`r A+C`$ games and losing $l=B+D=`r B+D`$ games,
from which we would obtain $\hat{p_1}=`r A+C`/`r A+B+C+D`$; a
likelihood ratio for $H_0\colon p_1=0.5$ would be

@@

@agresti2002 (p438) considers a dataset of seven baseball teams who
play one another repeatedly.  Each game is played at the home ground
of one team, the other playing away.  The dataset is as follows:

```{r,label=makeAgrestimatrix}
baseball_table <- matrix(c(
NA,   4+3i, 4+2i, 4+3i, 6+1i, 4+2i, 6+0i,
3+3i, NA  , 4+2i, 4+3i, 6+0i, 6+1i, 4+3i,
2+5i, 4+3i, NA  , 2+4i, 4+3i, 4+2i, 6+0i,
3+3i, 5+1i, 2+5i, NA  , 4+3i, 4+2i, 6+1i,
5+1i, 2+5i, 3+3i, 4+2i, NA  , 5+2i, 6+0i,
2+5i, 3+3i, 3+4i, 4+3i, 4+2i, NA  , 2+4i,
2+5i, 1+5i, 1+6i, 2+4i, 1+6i, 3+4i, NA),7,7)
teams <- c("Milwaukee", "Detroit", "Toronto", "New York", "Boston","Cleveland","Baltimore")
rownames(baseball_table) <- teams
colnames(baseball_table) <- teams
M <- baseball_table # saves typing
M # for convenience
```
